### 2021-02-18 evaluation.tex
Add section on input problem format and preprocessing

>>>>

\subsubsection{Input problems}

The raw input problems are assumed to be specified in the \gls{cnf} or the \gls{fof} fragment
of the \acrshort{tptp} language \cite{Sutcliffe2017}.
% http://www.tptp.org/TPTP/SyntaxBNF.html
Each problem is first preprocessed by Vampire:
\gls{fof} problems are converted into equisatisfiable \gls{cnf} problems,
and basic simplifications are performed.
\todo{FB: Explain in more detail or better terms.}
New symbols may be introduced into the problems during preprocessing.
We denote the preprocessed \gls{cnf} problem as $P = (\Sigma, \mathit{Cl})$,
where $\Sigma$ denotes the list of all predicate and function symbols of the problem,
and $\mathit{Cl}$ denotes a set of clauses over $\Sigma$ that constitute the problem.

In addition to the signature and the structure of the problem,
some metadata is extracted from the input problem to allow training a more efficient recommender.
First, each clause is annotated with its role in the problem,
which can be either axiom, assumption, or negated conjecture.
% This is simplified. There are actually 7 clause roles defined internally in Vampire,
% and it seems that only 4 of them are ever used in FOL problems:
% AXIOM, ASSUMPTION, CONJECTURE, NEGATED_CONJECTURE
% CONJECTURE is used in FOF problems and NEGATED_CONJECTURE is used in CNF problems,
% so the recommender can actually differentiate between these two forms.
Second, each symbol is annotated with two bits of data:
whether it was introduced into the problem during preprocessing,
and whether the symbol appears in a conjecture clause.
% Note that the second bit is redundant, since the clauses are annotated with their roles.
